---
title: "Using `cliquematch` in R"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

While [`cliquematch`](https://github.com/ahgamut/cliquematch) is a Python package, it can also be called from R by using [`reticulate`](https://rstudio.github.io/reticulate/). This document provides R snippets similar to the Python snippets in the `cliquematch` [documentation][docs].

[docs]: https://cliquematch.readthedocs.io/en/stable/user.html

We can set up our python environment from within RStudio by loading `reticulate` and selecting the python interpreter to use. I use the [`use_condaenv`][conda] function select a Python interpreter, but you can use `use_python` as well.

[conda]: https://rstudio.github.io/reticulate/reference/use_python.html

```{r}
library(reticulate)
use_condaenv(condaenv = "cm-dev")
# make sure you have installed cliquematch in python
cliquematch = import("cliquematch")
```

## Finding a maximum clique

Load a graph from a file: [cond-mat-2003.mtx](https://sparse.tamu.edu/Newman/cond-mat-2003) and find a maximum clique.

```{r}
G = cliquematch$Graph$from_file("./cond-mat-2003.mtx")
print(G)
```

We can also load a `Graph` using an adjacency matrix
(`Graph$from_adj_matrix`), an adjacency list
(`Graph$from_adj_list`), or a list of edges
(`Graph$from_edgelist`).  Once the `Graph` object has
been loaded, we can provide various parameters to search for a clique with `Graph$get_max_clique`:

```{r}
answer = G$get_max_clique(lower_bound=1L,upper_bound=1729L, 
                          time_limit=100, use_heuristic=T,
                          use_dfs=T, continue_search=F)
print(answer)
```


* A `lower_bound` and an `upper_bound` can be set for the size for clique.
* A `time_limit` can be set for the clique search. If time limits are not needed, set `0` as the limit.
* The `continue_search` parameter can be set to `TRUE` if the clique search terminated due to a time limit earlier.
* In case the graph is very large, to get a large clique quickly via aheuristic method, `use_heuristic` can be set to `True`, and
  `use_dfs` can be set to `False` to skip the depth-first
  search.
  
### Continuing an interrupted clique search

```{r}
while (!G$search_done) {
    answer = G$get_max_clique(lower_bound=1L,upper_bound=1729L, 
                              time_limit=100, use_heuristic=T, 
                              use_dfs=T, continue_search=T)
    # process answer if needed
}
print(answer)
```


## Clique enumeration

To obtain all cliques of a particular size: use the `all_cliques` method. Use [`iterate`][iter] or [`iter_next`][iter] to view the cliques one by one:

```{r}
cliques = G$all_cliques(size = 25L)
# iterate(cliques, f = print)
clq = iter_next(cliques, completed = NULL)
i = 0
while(!is.null(clq))
{
    
    print(clq)
    clq = iter_next(cliques, completed = NULL)
    i = i + 1
}
```

Thus the `cond-mat-2003` graph contains exactly one clique of size 25.

[iter]: https://rstudio.github.io/reticulate/reference/iterate.html
